\section{2021, January Mo.10^{th}}


Meeting: CG + RST + RS + GR 


\subsection{NeuroTwin}
\begin{itemize}
\item \textcolor{red}{Due date: 2/3/4… etc. How do you fix an exact day of delivery? Ex.: D5.1: 11th Feb 2021 (M2).
}
\item	\textcolor{red}{BIDMC is asking for assurances about compliance with GPDR to receive non-US data at BIDMC we could get a general statement signed across institutions ensuring everyone will comply with regulations when transferring data outside EU?}
\item \textcolor{red}{Consortium Agreement?} Deadline: End Feb.
\item \textcolor{red}{Data management plan?} D3.1. Deadline: Due month 3.
\item D5.1. \textbf{Questions}

"TEMPLATES: The following templates shall be provided to the consortium:\\
1.	Presentation template (.ppt and .key)\\
2.	Deliverable template (.docx)"\\
3.  This is the Quality Control Review Form (.docx)\\

$@$Giulio: Editable tables of the grant agreement? Folder Grant Agreement


\item Jordi- Suggestions before meeting him. General idea of what we want.Create Open Project or similar system for tasks (PRT system)[Coordinate with Jordi/IT] 



\end{itemize}


\subsection{Galvani}
\begin{itemize}
    \item Meeting Tu. $12^{th}$
    \item Periodicity?: Meetings to discuss strategy and matters at hand. (3months?¿?)
    \item Galvani Steering Committee Creation /Consortioum Agreement: \textbf{Rennes} (involving Tech Transfer agencies in Rennes and Marseille, Corporate Development in NE)
  

\end{itemize}

\subsection{Logistics \&  other stuff}
\begin{itemize}
    \item \textcolor{red}{STORAGE.} \href{https://docs.google.com/document/d/16v9LeHPt3SFdeu1WQeSEbZKQP_1lh1sQ4h05umlxRZ4/edit}{Check here}
    \item \textcolor{red}{Rules for joined document revisions, control of the revisions, Filenames conventions.}\href{https://docs.google.com/document/d/1TGVl9pppeMySwDjRnmjSmvmIVzkaIl4oBJjY9_VCWMU/edit} {Check here}
     \item Is there any confidential information about Galvani/ Neurotwin that cannot be shared w/ the group?

   
\end{itemize}

\subsection{TO DO:}
\begin{itemize}
   \item Integrate Gantt: pattern/colors/text in cells.
    \item \textbf{Feedback in D5.1}.
    \item Logbook Galvani-put it to Slack \textcolor{red}{prospective or retrospective?}.
    \item Technical notes (NT): Keep track of technical notes, which are under wirtting process, missing and future. Ex.:TN0145.
    \begin{itemize}
        \item Create an excel with names of people, TN, and status.
        \item Name convention and folders.
    \end{itemize}
    \item Send an email in a month from now to discuss literature (ask for literature to Emiliano, Giacomo...)
    \item Give feedback about mice database to Javier \footnote{https://imaging.org.au/AMBMC/Model}.
    \item Organize pathophysiology meeting (in a month from now 08.01.2021 $\rightarrow$ beginning of Feb. Tentative day: Fri. 5$^{th}$)
    \item Neurotwin: make a compact calendar with deliverables (D) and milestones (MS).
    \item \textbf{Skat - Cerverus}    
    \item High level gantt: Deadlines to think about.
    \begin{itemize}
        \item 1st Week February: Project Management System.
        \item Last week February: Implemented Project Management System.
        \item Coordinate w/ Jordi and David.
    \end{itemize}
    
\end{itemize}

\subsection{DONE:}
\begin{itemize}
    \item Better solution to lunch.
    \item Rules for joined document revisions, control of the revisions, Filenames conventions.
    \item Last version: \href{https://www.dropbox.com/home/998%20-%20neurotwin.eu%20repository/05%20-%20Deliverables?preview=NEUROTWIN+Deliverable+-+D5.1+Quality+Guide_v1.7_CG.docx}{Deliverable D5.1}.
\end{itemize}