%This is a template for completing this Summary Guide.
%Make sure you always start a new file and you do not overwrite this template.

\section{2021, January Mo.18^{th}}


Meeting: People involved in the meeting.

\subsection{NeuroTwin}
\begin{itemize}
    \item aaaaaa
    \item aaaaa

\end{itemize}


\subsection{Galvani}
\begin{itemize}
    \item aaaaaa
    \item aaaaa

\end{itemize}

\subsection{Logistics \&  other stuff}
\begin{itemize}
    \item aaaaaa
    \item aaaaa

\end{itemize}


\subsection{TO DO:}
\begin{itemize}
    \item Logbook Galvani-put it to Slack \textcolor{red}{prospective or retrospective?}.
    \item Technical notes (NT): Keep track of technical notes, which are under wirtting process, missing and future. Ex.:TN0145.
    \begin{itemize}
        \item Create an excel with names of people, TN, and status.
        \item Name convention and folders.
    \end{itemize}
    \item Send an email in a month from now to discuss literature (ask for literature to Emiliano, Giacomo...) (in a month from now 08.01.2021 $\rightarrow$ beginning of Feb).
    \item Give feedback about mice database to Javier \footnote{https://imaging.org.au/AMBMC/Model}.
    \item Organize pathophysiology meeting (in a month from now 08.01.2021 $\rightarrow$ beginning of Feb. Tentative day: Fri. 5$^{th}$)
    \item Neurotwin: make a compact calendar with deliverables (D) and milestones (MS).
    \item \textbf{Skat - Cerverus}    
    \item High level gantt: Deadlines to think about.
    \begin{itemize}
        \item 1st Week February: Project Management System.
        \item Last week February: Implemented Project Management System.
        \item Coordinate w/ Jordi and David.
        
\item \textcolor{red}{Consortium Agreement?} Deadline: End Feb.
\item \textcolor{red}{Data management plan?} D3.1. Deadline: Due month 3.
\item D5.1. \textbf{Templates}:
\begin{itemize}
    \item 	Presentation template (.ppt and .key)
    \item Deliverable template (.docx)
    \item \textcolor{red}{Quality Control Review Form (.docx)????}
\end{itemize}

\end{itemize}

\end{itemize}

\subsection{DONE:}
\begin{itemize}
    \item Integrated Gannt: LINK
    \item Last version \href{https://www.dropbox.com/home/998%20-%20neurotwin.eu%20repository/05%20-%20Deliverables?preview=NEUROTWIN+Deliverable+-+D5.1+Quality+Guide_v1.7_CG.docx}{Deliverable D5.1}.
\end{itemize}