\section{2021, January Thu.7^{th}}

Meeting: CG + RST

\subsection{NeuroTwin}
\begin{itemize}
    \item Document Rosa spots.
    \item \href{https://www.dropbox.com/home/998%20-%20neurotwin.eu%20repository/05%20-%20Deliverables?preview=NEUROTWIN+Deliverable+-+D5.1+Quality+Guide_v1.6.docx}{Deliverable D5.1} Feedback?

    \item Theoretical
        \begin{itemize}
            \item Starsim System: HW?
         	\itemStimweaver algorithm: SW? Servicio Extra a parte de Starsim. No va necesariamente unido al Starsim. Patient specific/group Specific/ Generic.
            \item	Ising (Niko) / laNMM  (MT Roser).
            \item	Concepts criticality and normalization.
            \item	Paper Pallop 2016.
        \end{itemize}
\end{itemize}


\subsection{Galvani}
\begin{itemize}
    \item How? When? 12t task?
    \item \href{https://docs.google.com/document/d/1pW-zTeiSJdutUG7ir9rBoyD5eRubBpaRs16GNvNYou4/edit?ts=5ff6cca4   }{Galvani Lab tasks/ Project logbook}: Edit document and create a template. Modify Drive document and Remind to the team members to fill it!!!! 

\end{itemize}

\subsection{Logistics \& other stuff}
\begin{itemize}
    \item Position Laura López Galdo.
    \item Revise list of PM tasks.
    \item Role in Meetings: Keep track of discussions in meetings and save it to meetings folder.

\end{itemize}

\subsection{TO DO:}
\begin{itemize}
   \item Integrate Gantt\footnote{https://prezi.com/view/A4DTYXXpVsNqS1TuUwdb/}: pattern/colors/text in cells.
    \item \href{https://www.dropbox.com/home/998%20-%20neurotwin.eu%20repository/05%20-%20Deliverables?preview=NEUROTWIN+Deliverable+-+D5.1+Quality+Guide_v1.6.docx}{Deliverable D5.1} Feedback.
    \item Logbook Galvani-put it to Slack.
    \item Better solution to lunch.
    \item Technical notes (NT): Keep track of technical notes, which are under wirtting process, missing and future. Ex.:TN0145.
    \begin{itemize}
        \item Create an excel with names of people, TN, and status.
        \item Name convention and folders.
    \end{itemize}

\end{itemize}

\subsection{DONE:}
