\section{Other documents}
\subsection{Projects}
\subsubsection{Neurotwin}
\begin{itemize}
 \item \href{https://www.dropbox.com/home/998%20-%20neurotwin.eu%20repository/01%20-%20Neurotwin%20Starter%20Kit?preview=Grant+Agreement-101017716-Neurotwin.pdf}{NeuroTwin Grant Agreement.}
 \item \href{https://www.dropbox.com/home/998%20-%20neurotwin.eu%20repository/01%20-%20Neurotwin%20Starter%20Kit?preview=Grant+Agreement-101017716-Neurotwin+TECH.pdf}{NeuroTwin Grant Agreement TECH (short).}
 \item \href{https://www.dropbox.com/home/009%20-%20Neuroelectrics%20Research%20WORK%20AREA/002%20-%20Neurotwin/101%20-%20Neurotwin%20Data%20Management%20Plan/from%20Luminous}{NeuroTwin Data Management Plan.}
 \item \href{https://www.dropbox.com/home/009%20-%20Neuroelectrics%20Research%20WORK%20AREA/002%20-%20Neurotwin/102%20-%20Neurotwin%20Consortium%20Agreement}{NeuroTwin Consortium Agreement.}
 \item \href{https://docs.google.com/document/d/1lEjSbhkZhggJMzSBceajwg3VIAWfD3EKFGuKd5JcIPM/edit}{Neurotwin Web Content.}
 \item \href{https://prezi.com/view/A4DTYXXpVsNqS1TuUwdb/}{Gantt Roser Prezi}
 \item \href{https://docs.google.com/spreadsheets/d/1TWLecaDlCCRT2Sj8MxZY4WaqSHaYyOZjTOToTy9Fnog/edit#gid=0}{Neurotwin directory.}
\end{itemize}
\begin{subsubsub}
\subsubsection{Deliverables}
\begin{itemize}
    \item \href{https://www.dropbox.com/home/998%20-%20neurotwin.eu%20repository/05%20-%20Deliverables?preview=NEUROTWIN+Deliverable+-+D5.1+Quality+Guide_v1.7_CG.docx}{Deliverable D5.1} (Last Version).
\end{itemize}
\end{subsubsub}

\subsubsection{Galvani}
\begin{itemize}
\item \href{https://www.dropbox.com/home/999%20-%20galvani-lab.eu%20repository/01%20-%20Galvani%20Basic%20Starter%20Kit?preview=Galvani+Tech+Proposal+855109--SEALED-PROPOSAL+short.pdf}{Galvani Grant Agreement TECH (short).}
    \item \href{https://docs.google.com/document/d/18_DfI75pC1e6bMpWSiBY7LVz0cBSdLIWyHygTgJ6p3w/edit}{Galvani Lab. Tasks.}
    \item \href{https://docs.google.com/spreadsheets/d/14srwfkr06nShSOCOmbv2nUXXlONLYjd6/edit?rtpof=true#gid=1839498795}{Galvani Gantt.}
     \item \href{https://docs.google.com/spreadsheets/d/1hmYrOKPDdvS4GNvrOgNENP8p-WfLTDdvGxLtxY_3WpU/edit#gid=0}{Galvani directory.}
\end{itemize}

\subsection{Other documents}
\begin{itemize}
   \item \href{https://docs.google.com/document/d/1TGVl9pppeMySwDjRnmjSmvmIVzkaIl4oBJjY9_VCWMU/edit?usp=sharing}{Rules for joined document revisions.}
   \item \href{https://docs.google.com/document/d/1k3vi7rj7HX7gRnTSQ9_zHMdyylKWJEN0YF3pZPfBDv0/edit}{Don´t panic guide.}
  \item \href{https://docs.google.com/document/d/1pyfM1j0SD_pPCVkUv2lWP6-E2Cya8ucYQ6GsUHYTrDE/edit#heading=h.axrlnzwlxave}{Data Management Plan.} 
  \item \href{https://docs.google.com/spreadsheets/d/10FZQ_QXZLdQijgOvBLNV6e2u1zObHv1MfcH_tUQ954g/edit#gid=1824133226}{Clinical research Overview.}
  \item \href{https://docs.google.com/spreadsheets/d/1-9uVHSc9v8hJlkRH3YDWJ-7bG6dIIWNw1KTHn9ufva4/edit#gid=2120321454}{NE Grants.}
  \item \href{https://docs.google.com/spreadsheets/d/181xnkBHL-Oe6InU_A1kzRPJXk24cG3IVgs6_l0440BA/edit#gid=0}{NE research project list}
\end{itemize}